---
title: "Pedagogy model"
output:
  html_document:
    theme: spacelab
    toc: yes
  pdf_document:
    toc: yes
---

```{r Load data and packages, echo=FALSE}
library(plyr, quietly=T, warn.conflicts=F)
library(dplyr, quietly=T, warn.conflicts=F)
library(ggplot2, quietly=T, warn.conflicts=F)
library(ggvis, quietly=T, warn.conflicts=F)
library(tidyr, quietly=T, warn.conflicts=F)
library(knitr, quietly=T, warn.conflicts=F)
library(boot, quietly=T, warn.conflicts=F)
library(forcats, quietly=T, warn.conflicts=F)
setwd("~/Documents/Projects/Models/Pedagogy/Pedagogy/FinalData_ExpUnc/")
data <- read.csv("Model_Betas.csv") %>% tbl_df %>% mutate(Model=paste(LearnC,LearnR,DiscoverC,DiscoverR))
data$Condition<-as.character(data$Condition)
data$ExploreProb<-factor(data$ExploreProb)
levels(data$ExploreProb)=c(".3 Exploration",".5 Exploration",".7 Exploration",".99 Exploration")
levels(data$Decision)=c("Either","Red toy","Yellow toy")

RangeLimit=87

data <- data %>% filter(RedToyReward<=RangeLimit,YellowToyReward<=RangeLimit)

# LEFT version
ParamA = 1.875
ParamB = 1

# MIDDLE version
#ParamA = 6
#ParamB = 4.15

# RIGHT version
ParamA = 10
ParamB = 7.5274

# First condition has rewards inverted inverted, so split:
dataA = data %>% filter(Condition == "1: R&C")
dataA <- dataA %>% mutate(prob=dbeta(RedToyReward/RangeLimit,ParamB,ParamA)*dbeta(YellowToyReward/RangeLimit,ParamA,ParamB))
dataB = data %>% filter(Condition != "1: R&C")
dataB <- dataB %>% mutate(prob=dbeta(RedToyReward/RangeLimit,ParamA,ParamB)*dbeta(YellowToyReward/RangeLimit,ParamB,ParamA))

data = rbind(dataA,dataB)
rm(dataA,dataB)

Summarydata <- data %>%
  dplyr::group_by(ExploreProb, Condition, Model, Decision) %>%
  dplyr::summarise(Percentage=sum(prob))

# We have some entries missing and we need them!
NullProbs <- Summarydata %>% select(-Percentage) %>% table %>% data.frame %>% filter(Freq==0) %>%
  dplyr::rename(Percentage=Freq)

Summarydata <- rbind(ungroup(Summarydata),NullProbs)

# Create alternate data frame where either gets split into the other two categories (as children will choose at random).
ConcreteChoices <- Summarydata %>% filter(Decision %in% c("Yellow toy","Red toy"))
NoPrefChoices <- Summarydata %>% filter(Decision %in% c("Either")) %>% mutate(PercAdd=Percentage/2) %>% select(-Percentage,-Decision)

Simpledata <- full_join(ConcreteChoices,NoPrefChoices,by=c("ExploreProb","Condition","Model")) %>%
  mutate(Perc=Percentage+PercAdd) %>% select(-Percentage,-PercAdd) %>%
  group_by(ExploreProb,Condition,Model) %>% do(data.frame(
    Decision=.$Decision,
    Perc=.$Perc*100/sum(.$Perc)
  ))
```

# Full model predictions

Model predictions as a function of exploration certainty. Values 0.25, and 0.75 indicate the probability that the learner will explore the untaught toy.


```{r MegaSummaryb, echo=FALSE, fig.width = 15, fig.height = 5}
ModelNames = data.frame(
  Model=c("1 1 1 1","1 0 1 0","0 1 0 1","1 1 0 0","0 0 1 1"),
  ModelName=c("Full model", "Costs-Only", "Rewards-Only", "Instruction-Only", "Exploration-Only")
)
ModelNames$ModelName = factor(ModelNames$ModelName, levels=c("Full model","Costs-Only","Rewards-Only","Instruction-Only","Exploration-Only"))
Tempdat <- full_join(Simpledata,ModelNames,by="Model") %>%
  ungroup() %>% dplyr::select(-Model) %>% dplyr::rename(Model=ModelName)
Tempdat$Decision<-as.character(Tempdat$Decision)
Noise = 0.1
Tempdat$Perc = Tempdat$Perc*(1-Noise)+50*Noise
Tempdat %>% ggplot(aes(x=Condition,y=Perc,fill=Decision))+geom_bar(stat="identity")+facet_grid(Model~ExploreProb)+theme_bw()+scale_fill_manual(values=c("#C7363D","#EBE549"))+scale_y_continuous("Percentage\nof choices")
#Tempdat %>% filter(ExploreProb==".5 Exploration") %>% spread(Model,Perc) %>% write.csv("Results.csv",row.names=F)
```

# Model fits. Using 50% exploration chance.

In each plot, entry i,j (row i, column j) shows the likelihood of model i generating the empirical data divided by the likelihood of model j generating the empirical data. Thus, values above 1 (green color-coded) indicate that the row model has a higher likelihood of generating the empirical data than the column model. Conversely, values below 1 (red color-coded) indicate that the row model has a lower likelihood of generating the empirical data than the column model. Values equal to 1 (blue color-coded) indicate both models are equally likely to have generated the data. For each section, alpha indicates the probability that participants get distracted and respond at chance.

As the plots above show, the full model outperforms all other alternative models for a wide range of noise parameters.

## Alpha = 0.01

```{r GetLikA, echo=FALSE, fig.width = 10}
# Get probability of choosing red toy.
NoiseParam=0.01
Probs <- Simpledata %>% ungroup %>% filter(ExploreProb==".5 Exploration",Decision=="Red toy") %>% mutate(Prob=Perc/100) %>% select(-ExploreProb,-Decision,-Perc)
# Load experiment results
Empirical<-read.csv("EmpiricalData.csv") %>% tbl_df
Empirical$Condition<-as.character(Empirical$Condition)
Probs$Condition<-as.character(Probs$Condition)
Probs <- full_join(Probs,Empirical,by="Condition") %>%
  dplyr::mutate(NoiseProb=(1-NoiseParam)*Prob+NoiseParam/2)
Probs <- plyr::ddply(Probs,c("Condition","Model","Prob","RedToy","SampleSize","NoiseProb"),function(x){
  dbinom(x$RedToy,x$SampleSize,x$NoiseProb)}) %>%
  dplyr::rename(Likelihood=V1) %>% tbl_df
# Now get the likelihood of each model producing the whole dataset.
FinalProbs<-Probs %>% dplyr::group_by(Model) %>% dplyr::summarise(Likelihood=prod(Likelihood))

# Order is: 3,2,4,1,5. Corresponding to: costs only, rewards only, instruction-only, exploration-only, and full model
LikelihoodRatios=data.frame(
  ModelA=rep(c("Costs-Only","Rewards-Only","Instruction-Only","Exploration-Only","Full model"),each=5),
  ModelB=rep(c("Costs-Only","Rewards-Only","Instruction-Only","Exploration-Only","Full model"),5),
  LR=c(
    FinalProbs[3,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[3,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[3,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[3,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[3,]$Likelihood/FinalProbs[5,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[5,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[5,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[5,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[5,]$Likelihood
)
  ) %>% mutate(Performance=ifelse(LR>1,"Better",ifelse(LR<1,"Worse","Equal"))) %>% tbl_df

LikelihoodRatios$ModelA=factor(LikelihoodRatios$ModelA,levels(LikelihoodRatios$ModelA)[c(2,4,3,5,1)])
LikelihoodRatios$ModelB=factor(LikelihoodRatios$ModelB,levels(LikelihoodRatios$ModelB)[c(1,5,3,4,2)])

T1<-LikelihoodRatios %>% filter(ModelA=="Full model") %>% mutate(Noise=0.01)

LikelihoodRatios %>% ggplot(aes(x=ModelB,y=ModelA,fill=Performance,label=format(LR)))+geom_tile()+geom_text()+theme_bw()+scale_fill_manual(values=c("#3AB551","#35A7F2","#B53A40"))+scale_y_discrete("Nominator")+scale_x_discrete("Denominator")
```

## Alpha = 0.05

```{r GetLikB, echo=FALSE, fig.width = 10}
# Get probability of choosing red toy.
NoiseParam=0.05
Probs <- Simpledata %>% ungroup %>% filter(ExploreProb==".5 Exploration",Decision=="Red toy") %>% mutate(Prob=Perc/100) %>% select(-ExploreProb,-Decision,-Perc)
# Load experiment results
Empirical<-read.csv("EmpiricalData.csv") %>% tbl_df
Empirical$Condition<-as.character(Empirical$Condition)
Probs$Condition<-as.character(Probs$Condition)
Probs <- full_join(Probs,Empirical,by="Condition") %>%
  dplyr::mutate(NoiseProb=(1-NoiseParam)*Prob+NoiseParam/2)
Probs <- plyr::ddply(Probs,c("Condition","Model","Prob","RedToy","SampleSize","NoiseProb"),function(x){
  dbinom(x$RedToy,x$SampleSize,x$NoiseProb)}) %>%
  dplyr::rename(Likelihood=V1) %>% tbl_df
# Now get the likelihood of each model producing the whole dataset.
FinalProbs<-Probs %>% dplyr::group_by(Model) %>% dplyr::summarise(Likelihood=prod(Likelihood))

# Costs only first
LikelihoodRatios=data.frame(
  ModelA=rep(c("Costs-Only","Rewards-Only","Instruction-Only","Exploration-Only","Full model"),each=5),
  ModelB=rep(c("Costs-Only","Rewards-Only","Instruction-Only","Exploration-Only","Full model"),5),
  LR=c(
    FinalProbs[3,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[3,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[3,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[3,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[3,]$Likelihood/FinalProbs[5,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[5,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[5,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[5,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[5,]$Likelihood
)
  ) %>% mutate(Performance=ifelse(LR>1,"Better",ifelse(LR<1,"Worse","Equal"))) %>% tbl_df

LikelihoodRatios$ModelA=factor(LikelihoodRatios$ModelA,levels(LikelihoodRatios$ModelA)[c(2,4,3,5,1)])
LikelihoodRatios$ModelB=factor(LikelihoodRatios$ModelB,levels(LikelihoodRatios$ModelB)[c(1,5,3,4,2)])

T2<-LikelihoodRatios %>% filter(ModelA=="Full model") %>% mutate(Noise=0.05)

LikelihoodRatios %>% ggplot(aes(x=ModelB,y=ModelA,fill=Performance,label=format(LR)))+geom_tile()+geom_text()+theme_bw()+scale_fill_manual(values=c("#3AB551","#35A7F2","#B53A40"))+scale_y_discrete("Nominator")+scale_x_discrete("Denominator")
```

## Alpha = 0.1

```{r GetLikC, echo=FALSE, fig.width = 10}
# Get probability of choosing red toy.
NoiseParam=0.1
Probs <- Simpledata %>% ungroup %>% filter(ExploreProb==".5 Exploration",Decision=="Red toy") %>% mutate(Prob=Perc/100) %>% select(-ExploreProb,-Decision,-Perc)
# Load experiment results
Empirical<-read.csv("EmpiricalData.csv") %>% tbl_df
Empirical$Condition<-as.character(Empirical$Condition)
Probs$Condition<-as.character(Probs$Condition)
Probs <- full_join(Probs,Empirical,by="Condition") %>%
  dplyr::mutate(NoiseProb=(1-NoiseParam)*Prob+NoiseParam/2)
Probs <- plyr::ddply(Probs,c("Condition","Model","Prob","RedToy","SampleSize","NoiseProb"),function(x){
  dbinom(x$RedToy,x$SampleSize,x$NoiseProb)}) %>%
  dplyr::rename(Likelihood=V1) %>% tbl_df
# Now get the likelihood of each model producing the whole dataset.
FinalProbs<-Probs %>% dplyr::group_by(Model) %>% dplyr::summarise(Likelihood=prod(Likelihood))

# Costs only first
LikelihoodRatios=data.frame(
  ModelA=rep(c("Costs-Only","Rewards-Only","Instruction-Only","Exploration-Only","Full model"),each=5),
  ModelB=rep(c("Costs-Only","Rewards-Only","Instruction-Only","Exploration-Only","Full model"),5),
  LR=c(
    FinalProbs[3,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[3,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[3,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[3,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[3,]$Likelihood/FinalProbs[5,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[5,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[5,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[5,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[5,]$Likelihood
)
  ) %>% mutate(Performance=ifelse(LR>1,"Better",ifelse(LR<1,"Worse","Equal"))) %>% tbl_df

LikelihoodRatios$ModelA=factor(LikelihoodRatios$ModelA,levels(LikelihoodRatios$ModelA)[c(2,4,3,5,1)])
LikelihoodRatios$ModelB=factor(LikelihoodRatios$ModelB,levels(LikelihoodRatios$ModelB)[c(1,5,3,4,2)])

T3<-LikelihoodRatios %>% filter(ModelA=="Full model") %>% mutate(Noise=0.1)

DetailedProbs <- Probs

LikelihoodRatios %>% ggplot(aes(x=ModelB,y=ModelA,fill=Performance,label=format(LR)))+geom_tile()+geom_text()+theme_bw()+scale_fill_manual(values=c("#3AB551","#35A7F2","#B53A40"))+scale_y_discrete("Nominator")+scale_x_discrete("Denominator")
```

## Alpha = 0.2

```{r GetLik2, echo=FALSE, fig.width = 10}
# Get probability of choosing red toy.
NoiseParam=0.2
Probs <- Simpledata %>% ungroup %>% filter(ExploreProb==".5 Exploration",Decision=="Red toy") %>% mutate(Prob=Perc/100) %>% select(-ExploreProb,-Decision,-Perc)
# Load experiment results
Empirical<-read.csv("EmpiricalData.csv") %>% tbl_df
Empirical$Condition<-as.character(Empirical$Condition)
Probs$Condition<-as.character(Probs$Condition)
Probs <- full_join(Probs,Empirical,by="Condition") %>%
  dplyr::mutate(NoiseProb=(1-NoiseParam)*Prob+NoiseParam/2)
Probs <- plyr::ddply(Probs,c("Condition","Model","Prob","RedToy","SampleSize","NoiseProb"),function(x){
  dbinom(x$RedToy,x$SampleSize,x$NoiseProb)}) %>%
  dplyr::rename(Likelihood=V1) %>% tbl_df
# Now get the likelihood of each model producing the whole dataset.
FinalProbs<-Probs %>% dplyr::group_by(Model) %>% dplyr::summarise(Likelihood=prod(Likelihood))

# Costs only first
LikelihoodRatios=data.frame(
  ModelA=rep(c("Costs-Only","Rewards-Only","Instruction-Only","Exploration-Only","Full model"),each=5),
  ModelB=rep(c("Costs-Only","Rewards-Only","Instruction-Only","Exploration-Only","Full model"),5),
  LR=c(
    FinalProbs[3,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[3,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[3,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[3,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[3,]$Likelihood/FinalProbs[5,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[5,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[5,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[5,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[5,]$Likelihood
)
  ) %>% mutate(Performance=ifelse(LR>1,"Better",ifelse(LR<1,"Worse","Equal"))) %>% tbl_df

LikelihoodRatios$ModelA=factor(LikelihoodRatios$ModelA,levels(LikelihoodRatios$ModelA)[c(2,4,3,5,1)])
LikelihoodRatios$ModelB=factor(LikelihoodRatios$ModelB,levels(LikelihoodRatios$ModelB)[c(1,5,3,4,2)])

T4<-LikelihoodRatios %>% filter(ModelA=="Full model") %>% mutate(Noise=0.2)

LikelihoodRatios %>% ggplot(aes(x=ModelB,y=ModelA,fill=Performance,label=format(LR)))+geom_tile()+geom_text()+theme_bw()+scale_fill_manual(values=c("#3AB551","#35A7F2","#B53A40"))+scale_y_discrete("Nominator")+scale_x_discrete("Denominator")
```

## Alpha = 0.3

```{r GetLik3, echo=FALSE, fig.width = 10}
# Get probability of choosing red toy.
NoiseParam=0.3
Probs <- Simpledata %>% ungroup %>% filter(ExploreProb==".5 Exploration",Decision=="Red toy") %>% mutate(Prob=Perc/100) %>% select(-ExploreProb,-Decision,-Perc)
# Load experiment results
Empirical<-read.csv("EmpiricalData.csv") %>% tbl_df
Empirical$Condition<-as.character(Empirical$Condition)
Probs$Condition<-as.character(Probs$Condition)
Probs <- full_join(Probs,Empirical,by="Condition") %>%
  dplyr::mutate(NoiseProb=(1-NoiseParam)*Prob+NoiseParam/2)
Probs <- plyr::ddply(Probs,c("Condition","Model","Prob","RedToy","SampleSize","NoiseProb"),function(x){
  dbinom(x$RedToy,x$SampleSize,x$NoiseProb)}) %>%
  dplyr::rename(Likelihood=V1) %>% tbl_df
# Now get the likelihood of each model producing the whole dataset.
FinalProbs<-Probs %>% dplyr::group_by(Model) %>% dplyr::summarise(Likelihood=prod(Likelihood))

# Costs only first
LikelihoodRatios=data.frame(
  ModelA=rep(c("Costs-Only","Rewards-Only","Instruction-Only","Exploration-Only","Full model"),each=5),
  ModelB=rep(c("Costs-Only","Rewards-Only","Instruction-Only","Exploration-Only","Full model"),5),
  LR=c(
    FinalProbs[3,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[3,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[3,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[3,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[3,]$Likelihood/FinalProbs[5,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[5,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[5,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[5,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[5,]$Likelihood
)
  ) %>% mutate(Performance=ifelse(LR>1,"Better",ifelse(LR<1,"Worse","Equal"))) %>% tbl_df

LikelihoodRatios$ModelA=factor(LikelihoodRatios$ModelA,levels(LikelihoodRatios$ModelA)[c(2,4,3,5,1)])
LikelihoodRatios$ModelB=factor(LikelihoodRatios$ModelB,levels(LikelihoodRatios$ModelB)[c(1,5,3,4,2)])

T5<-LikelihoodRatios %>% filter(ModelA=="Full model") %>% mutate(Noise=0.3)

LikelihoodRatios %>% ggplot(aes(x=ModelB,y=ModelA,fill=Performance,label=format(LR)))+geom_tile()+geom_text()+theme_bw()+scale_fill_manual(values=c("#3AB551","#35A7F2","#B53A40"))+scale_y_discrete("Nominator")+scale_x_discrete("Denominator")
```

## Alpha = 0.4

```{r GetLik4, echo=FALSE, fig.width = 10}
# Get probability of choosing red toy.
NoiseParam=0.4
Probs <- Simpledata %>% ungroup %>% filter(ExploreProb==".5 Exploration",Decision=="Red toy") %>% mutate(Prob=Perc/100) %>% select(-ExploreProb,-Decision,-Perc)
# Load experiment results
Empirical<-read.csv("EmpiricalData.csv") %>% tbl_df
Empirical$Condition<-as.character(Empirical$Condition)
Probs$Condition<-as.character(Probs$Condition)
Probs <- full_join(Probs,Empirical,by="Condition") %>%
  dplyr::mutate(NoiseProb=(1-NoiseParam)*Prob+NoiseParam/2)
Probs <- plyr::ddply(Probs,c("Condition","Model","Prob","RedToy","SampleSize","NoiseProb"),function(x){
  dbinom(x$RedToy,x$SampleSize,x$NoiseProb)}) %>%
  dplyr::rename(Likelihood=V1) %>% tbl_df
# Now get the likelihood of each model producing the whole dataset.
FinalProbs<-Probs %>% dplyr::group_by(Model) %>% dplyr::summarise(Likelihood=prod(Likelihood))

# Costs only first
LikelihoodRatios=data.frame(
  ModelA=rep(c("Costs-Only","Rewards-Only","Instruction-Only","Exploration-Only","Full model"),each=5),
  ModelB=rep(c("Costs-Only","Rewards-Only","Instruction-Only","Exploration-Only","Full model"),5),
  LR=c(
    FinalProbs[3,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[3,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[3,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[3,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[3,]$Likelihood/FinalProbs[5,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[5,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[5,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[5,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[5,]$Likelihood
)
  ) %>% mutate(Performance=ifelse(LR>1,"Better",ifelse(LR<1,"Worse","Equal"))) %>% tbl_df

LikelihoodRatios$ModelA=factor(LikelihoodRatios$ModelA,levels(LikelihoodRatios$ModelA)[c(2,4,3,5,1)])
LikelihoodRatios$ModelB=factor(LikelihoodRatios$ModelB,levels(LikelihoodRatios$ModelB)[c(1,5,3,4,2)])

T6<-LikelihoodRatios %>% filter(ModelA=="Full model") %>% mutate(Noise=0.4)

LikelihoodRatios %>% ggplot(aes(x=ModelB,y=ModelA,fill=Performance,label=format(LR)))+geom_tile()+geom_text()+theme_bw()+scale_fill_manual(values=c("#3AB551","#35A7F2","#B53A40"))+scale_y_discrete("Nominator")+scale_x_discrete("Denominator")
```

## Alpha = 0.5

```{r GetLi8, echo=FALSE, fig.width = 10}
# Get probability of choosing red toy.
NoiseParam=0.5
Probs <- Simpledata %>% ungroup %>% filter(ExploreProb==".5 Exploration",Decision=="Red toy") %>% mutate(Prob=Perc/100) %>% select(-ExploreProb,-Decision,-Perc)
# Load experiment results
Empirical<-read.csv("EmpiricalData.csv") %>% tbl_df
Empirical$Condition<-as.character(Empirical$Condition)
Probs$Condition<-as.character(Probs$Condition)
Probs <- full_join(Probs,Empirical,by="Condition") %>%
  dplyr::mutate(NoiseProb=(1-NoiseParam)*Prob+NoiseParam/2)
Probs <- plyr::ddply(Probs,c("Condition","Model","Prob","RedToy","SampleSize","NoiseProb"),function(x){
  dbinom(x$RedToy,x$SampleSize,x$NoiseProb)}) %>%
  dplyr::rename(Likelihood=V1) %>% tbl_df
# Now get the likelihood of each model producing the whole dataset.
FinalProbs<-Probs %>% dplyr::group_by(Model) %>% dplyr::summarise(Likelihood=prod(Likelihood))

# Costs only first
LikelihoodRatios=data.frame(
  ModelA=rep(c("Costs-Only","Rewards-Only","Instruction-Only","Exploration-Only","Full model"),each=5),
  ModelB=rep(c("Costs-Only","Rewards-Only","Instruction-Only","Exploration-Only","Full model"),5),
  LR=c(
    FinalProbs[3,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[3,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[3,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[3,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[3,]$Likelihood/FinalProbs[5,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[2,]$Likelihood/FinalProbs[5,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[4,]$Likelihood/FinalProbs[5,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[1,]$Likelihood/FinalProbs[5,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[3,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[2,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[4,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[1,]$Likelihood,
FinalProbs[5,]$Likelihood/FinalProbs[5,]$Likelihood
)
  ) %>% mutate(Performance=ifelse(LR>1,"Better",ifelse(LR<1,"Worse","Equal"))) %>% tbl_df

LikelihoodRatios$ModelA=factor(LikelihoodRatios$ModelA,levels(LikelihoodRatios$ModelA)[c(2,4,3,5,1)])
LikelihoodRatios$ModelB=factor(LikelihoodRatios$ModelB,levels(LikelihoodRatios$ModelB)[c(1,5,3,4,2)])

T7<-LikelihoodRatios %>% filter(ModelA=="Full model") %>% mutate(Noise=0.5)

LikelihoodRatios %>% ggplot(aes(x=ModelB,y=ModelA,fill=Performance,label=format(LR)))+geom_tile()+geom_text()+theme_bw()+scale_fill_manual(values=c("#3AB551","#35A7F2","#B53A40"))+scale_y_discrete("Nominator")+scale_x_discrete("Denominator")
```

# Likelihood per condition

Likelihood of each model generating the data of each individual condition when exploration uncertainty = 0.5 and noise = 0.1

```{r DetailedProbs, echo=FALSE, fig.width = 15}
# Get probability of choosing red toy.
DetailedProbs$Model<-factor(DetailedProbs$Model)
levels(DetailedProbs$Model)=c("Exploration-Only","Rewards-Only","Costs-Only","Instruction-Only","Full model")
DetailedProbs %>% ggplot(aes(x=Condition,y=Model,fill=Likelihood,label=Likelihood))+geom_tile()+geom_text()+theme_bw()
```

# Noise summary

log(L(Data|FullModel)/L(Data|AlternativeModel)) as a function of different noise parameters. All values are above 0 (meaning that the likelihood ratio is greater than 1), showing that the full model explains the data better than all alternative models, independent of the noise parameter.

```{r NoiseSum, echo=FALSE, fig.width = 10}
# Get probability of choosing red toy.
NoiseSum<-rbind(T1,T2,T3,T4,T5,T6,T7)
NoiseSum %>% filter(ModelB!="Full model") %>% ggplot(aes(x=ModelB,y=log(LR),color=Noise,group=Noise))+geom_point(size=3)+theme_bw()+geom_line()+scale_x_discrete("Alternative model")+scale_y_continuous("Log-likelihood between full model\nand alternative models")
```

